Real Time Adaptive Shape Reconstruction for Asteroid Landing

### 2018-10-25 manuscript.tex
Update author

\author{Shankar Kulumani \footnote{PhD, Mechanical and Aerospace Engineering, Address/Mail Stop, and AIAA Member Grade (if any) for first author.} and Taeyoung Lee \footnote{Associate Professor, Department Name, Address/Mail Stop, and AIAA Member Grade (if any) for second author.}}
\affil{Goerge Washington University, Washington, DC, 20052}

>>>>

\author{Shankar Kulumani \footnote{PhD, Mechanical and Aerospace Engineering, \href{skulumani@gwu.edu}{mailto:skulumani@gwu.edu}}
and
Taeyoung Lee \footnote{Associate Professor, Mechanical and Aerospace Engineering, \href{tylee@gwu.edu}{mailto:tylee@gwu.edu}}}
\affil{Goerge Washington University, Washington, DC, 20052}
